---
title: "Final Report - Analyzing Cosponsorship"
author: "Lorenzo Maria Casale & Matteo Machiorlatti"
date: "15/09/2024"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
# Load required libraries
library(readr)
library(dplyr)
library(ggplot2)
library(lmtest)
library(ivreg)
library(knitr)
library(kableExtra)
library(tidyr)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(sandwich)
library(stargazer)
library(rmarkdown)
library(sandwich)  # For robust standard errors
library(lmtest)    # For coeftest function
```


In this research report we quickly show the determinants of the cosponsorship at bills level.

We firstly scraped the data related to the bills presented to the House of Congress in the 2010s.

For each bill, we collect the ID of the Congress they were introduced, some bill-specific information, (i.e. the bill's url, the title of the proposal, the committee interested by the bill - e.g. Energy or Housing - and the status - e.g. Passed House, or Law), the sponsor, namely the person who introduced the bill, her party, her state of election, as well as the district of election and, then, we also collected information on cosponsors, namely who publicly support the law introduced, and apart from gathering the number of co-sponsors, we also observe how many of those are sharing the party affiliation and/or the state of origin. 

```{r dataprep, echo=FALSE, message=FALSE, warning=FALSE}

#input_file <- file.path(dirname(getwd()), "data", snakemake@input[[2]])
input_file <- file.path(dirname(getwd()), "data", "bills_data_final.csv")
output_file <- file.path(dirname(getwd()), "results", "final_report.html")

## Appending all files
bills_data <- read.csv(input_file)

## Adding 'year' column based on 'congress_id'
bills_data <- bills_data %>%
  mutate(year = case_when(
    congress_id == 112 ~ "2011-2012",
    congress_id == 113 ~ "2013-2014",
    congress_id == 114 ~ "2015-2016",
    congress_id == 115 ~ "2017-2018",
    congress_id == 116 ~ "2019-2020"
  ))

## Creating Census Region
W <- c("AK", "AZ", "CA", "CO", "HI", "ID", "MT", "NV", "NM", "OR", "UT", "WA", "WY")
S <- c("AL", "AR", "DE", "FL", "GA", "KY", "LA", "MD", "MS", "NC", "OK", "SC", "TN", "TX", "VA", "WV")
MW <- c("IL", "IN", "IA", "KS", "MI", "MN", "MO", "NE", "ND", "OH", "SD", "WI")
NE <- c("CT", "ME", "MA", "NH", "NJ", "NY", "PA", "RI", "VT")

# Combine lists into a named list
All <- list(W = W, S = S, MW = MW, NE = NE)
Reg <- c("West", "South", "Midwest", "Northeast")

# Assume bills_data is your data frame with a column `sponsor_state`
bills_data$sponsor_region <- NA

# Update the region based on state abbreviations
for (reg in names(All)) {
  bills_data$sponsor_region[bills_data$sponsor_state %in% All[[reg]]] <- reg
}

# Set any remaining NA values to "Others"
bills_data$sponsor_region[is.na(bills_data$sponsor_region)] <- "Others"

# Create is_law variable
bills_data$is_law <- ifelse(bills_data$status %in% c("Became Law", "Became Private Law"), 1, 0)

# Create is_passed variable
bills_data$is_passed <- ifelse(bills_data$status %in% c("Became Law", "Became Private Law", "Vetoed by President", "Failed to pass over veto", "Resolving Differences", "Passed House", "Passed Senate"), 1, 0)
```

# Descriptive Statistics

Table 1 - Descriptive Statistics of Bill Data by Sponsor Party - shows the number of bills by sponsor's party. Because of the negligible number of bills sponsored by independents (I) and liberals (L), we will focus only on Democrats (D) and Republicans (R)

```{r datadescr0, echo=FALSE, message=FALSE, warning=FALSE}
## Descriptive statistics with number of bills by sponsor_party
descriptive_stats <- bills_data %>% 
  group_by(sponsor_party) %>%
  summarise(
    `N. Bills` = n()  # Count of bills by sponsor_party
  )

descriptive_stats %>%
  kbl(caption = "Descriptive Statistics of Bill Data by Sponsor Party", digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE) %>%
  add_header_above(c(" " = 1, "Descriptive Stats" = 1)) %>%
  row_spec(0, bold = TRUE, extra_css = "border-bottom: 2px solid;")


bills_data <- bills_data %>%
  filter(sponsor_party %in% c("D", "R"))

bills_data <- bills_data %>%
  mutate(majority = case_when(
    sponsor_party == "R" & congress_id %in% c(112, 113, 114, 115) ~ 1,
    sponsor_party == "D" & congress_id == 116 ~ 1,
    TRUE ~ 0
  ))
```


Table 2. - Descriptive Statistics of Bill Data - presents summary statistics for the average number of cosponsors (Avg. N. Cosponsor) across all bills, as well as the average number of cosponsors from the same party, same state, and those belonging to the same party and state.

We can immediately observe how among the co-sponsors the vast majority share, as natural, the party with the co-sponsor itself.

On average 16 members play as bill's cosponsors, yet only 1.4 of those come from the same party and the same state, where the latter is clearly the limiting factor in the analysis.


```{r datadescr1, echo=FALSE, message=FALSE, warning=FALSE}
## Descriptive statistics all sample
descriptive_stats <- bills_data %>% 
  summarise(
    `Avg. N. Cosponsor` = mean(n_cosponsor, na.rm = TRUE),
    `Avg. N. Same Party Cosp.` = mean(same_party, na.rm = TRUE),
    `Avg. N. Same State Cosp.` = mean(same_state, na.rm = TRUE),
    `Avg. N. Same (Party x State) Cosp.` = mean(same_party_state, na.rm = TRUE)
  )
descriptive_stats %>%
  kbl(caption = "Descriptive Statistics of Bill Data", digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE) %>%
  add_header_above(c(" " = 1, "Descriptive Stats" = 3)) %>%
  row_spec(0, bold = TRUE, extra_css = "border-bottom: 2px solid;")
```


In Table 2 - Probability of Each Bill Status - we show that only a small portion becomes a law - slightly more than 3%. In general, however, 10% of the bills manages to surpass the first obstacle, namely the Congress' House. The rest is just merely introduced and no further steps are made.

```{r datadescr1b, echo=FALSE, message=FALSE, warning=FALSE}

## Descriptive statistics all sample - Passing Probability
status_probs <- bills_data %>%
  group_by(status) %>%
  summarise(`Probability` = n() / nrow(bills_data)) %>%
  mutate(status = factor(status, levels = c("Became Law", "Became Private Law", "Vetoed by President", 
                                            "Failed to pass over veto", "Resolving Differences", 
                                            "Passed House", "Passed Senate", "Failed House", "Introduced"))) %>%
  arrange(status)  # Arrange based on the custom factor order

status_probs %>%
  kbl(caption = "Probability of Each Bill Status", digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE) %>%
  row_spec(0, bold = TRUE, extra_css = "border-bottom: 2px solid;")
```

Down below, in Table 3 - Descriptive Statistics of Bill Data by Congress and Year - and Table 4 - Probability of Each Bill Status by Congress and Year - we replicate what we did in the 2 previous tables, but we show what happens when we split the data over congresses.

In general, we observe that it appears that the ratio of law passed - i.e. those which either became or law or managed to pass the House vote - is the highest in Congress 115, despite the number of co-sponsor is slightly smaller than almost all the other congresses available.

```{r datadescr2, echo=FALSE, message=FALSE, warning=FALSE}

## Descriptive statistics by congress_id
descriptive_stats_by_congress <- bills_data %>% 
  group_by(congress_id, year) %>%
  summarise(
    `Avg. N. Cosponsor` = mean(n_cosponsor, na.rm = TRUE),
    `Avg. N. Same Party Cosp.` = mean(same_party, na.rm = TRUE),
    `Avg. N. Same State Cosp.` = mean(same_state, na.rm = TRUE),
    `Avg. N. Same (Party x State) Cosp.` = mean(same_party_state, na.rm = TRUE)
  )

descriptive_stats_by_congress %>%
  kbl(caption = "Descriptive Statistics of Bill Data by Congress and Year", digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE)
```

```{r datadescr3, echo=FALSE, message=FALSE, warning=FALSE}

## Descriptive statistics by congress_id - Passing Probability

status_probs_by_congress <- bills_data %>%
  group_by(congress_id, year, status) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(congress_id, year) %>%
  mutate(total = sum(count), 
         `Probability` = count / total) %>%
  filter(status %in% c("Became Law", "Passed House", "Passed Senate", "Failed House", "Introduced")) %>%
  select(-count, -total)  # Remove intermediate columns if you don't need them


status_probs_wide <- status_probs_by_congress %>%
  unite("congress_year", congress_id, year, sep = " (") %>%
  mutate(congress_year = paste0(congress_year, ")")) %>%
  pivot_wider(
    names_from = congress_year, 
    values_from = Probability,
    values_fill = 0  # Fill any missing combinations with 0
  ) %>%
  arrange(match(status, c("Became Law", "Passed House", "Passed Senate", "Failed House", "Introduced")))

status_probs_wide %>%
  kbl(caption = "Probability of Each Bill Status by Congress and Year", digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE)
```


Table 5 - Probability of Bills Becoming Law by Party and Congress - is definetely more interesting, as it shows the probability of a bill becoming a law split by party. It appears that when leading - in bold - Republicans managed to exert their power more than Democrats. We can see, indeed, the big difference both with respect to their counterpart within congress and with respect to when they were the opposing force. On the other hand, when Democrats were leading the House of Congress, there was not a clear difference with respect to when they were the trailing force.

Because of the small  of Independents in 

```{r datadescr4, echo=FALSE, message=FALSE, warning=FALSE}

## Calculate the probability of a bill becoming law by party and congress

prob_by_party_congress <- bills_data %>%
  filter(sponsor_party %in% c("R", "D")) %>%
  group_by(congress_id, year, sponsor_party) %>%
  summarise(`Prob. Becoming Law` = mean(status == "Became Law", na.rm = TRUE), .groups = 'drop') %>%
  pivot_wider(names_from = sponsor_party, values_from = `Prob. Becoming Law`, values_fill = list(`Prob. Becoming Law` = 0)) %>%
  rename(Republican = R, Democrat = D)

prob_by_party_congress <- prob_by_party_congress %>%
  mutate(
    Republican = ifelse(congress_id != 116, cell_spec(round(Republican, 3), bold = TRUE), round(Republican, 3)),
    Democrat = ifelse(congress_id == 116, cell_spec(round(Democrat, 3), bold = TRUE), round(Democrat, 3))
  )

prob_by_party_congress %>%
  kbl(escape = FALSE, caption = "Probability of Bills Becoming Law by Party and Congress") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE) %>%
  add_header_above(c(" " = 2, "Probability of Becoming Law" = 2)) %>%
  row_spec(0, bold = TRUE, extra_css = "border-bottom: 2px solid;")
```


Here, in Figure 1 - Probability of Bills Becoming Law by State -, we show that, apart some peaks when Idaho and Mississippi representatives are proposing their bills, there are no clear differences among the states. This appears to be even truer when we compare states from the same Census Region. Each Census is recognizable because of each state's border. In yellow, there are the west states, in red the midwest, in green the south states, and finally in violet the north-east states.


```{r datadescr5, echo=FALSE, message=FALSE, warning=FALSE}

##  Load spatial data for US states
us_states <- rnaturalearth::ne_states(country = "United States of America", returnclass = "sf")

## Ensure state abbreviations in the bills_data match those in the spatial data
us_states <- us_states %>%
  mutate(sponsor_state = state.abb[match(name, state.name)]) %>%
  select(sponsor_state, geometry)

## Merge the state map with bills data
state_map <- us_states %>%
  left_join(bills_data %>%
              group_by(sponsor_state) %>%
              summarise(`Prob. Becoming Law` = mean(status == "Became Law", na.rm = TRUE), 
                        sponsor_region = first(sponsor_region)),
            by = "sponsor_state")

## Remove Alaska (AK) and Hawaii (HI) from the spatial data and bills data
state_map <- state_map %>%
  filter(!sponsor_state %in% c("AK", "HI"))

## Define the darkest color for each region
region_colors <- c(
  "W" = "#FFC500",   # Dark Orange for West
  "S" = "#009900",  # Dark Green for South
  "MW" = "#FF0000", # Dark Brown for Midwest
  "NE" = "#9999FF" # Dark Cyan for Northeast
)

## Add border colors to the data
state_map <- state_map %>%
  mutate(border_color = region_colors[sponsor_region])

## Create the map
ggplot(data = state_map) +
  geom_sf(aes(fill = `Prob. Becoming Law`, color = border_color), lwd = 1) +  # Increased border size
  scale_fill_gradientn(colors = c("#E0FFFF", "#36454F"), name = "Probability", labels = scales::number_format(accuracy = 0.01)
) + # Apply the gradient scale for probability
  scale_color_identity() +  # Use the colors defined in the data
  theme_minimal() +
  labs(title = "Probability of Bills Becoming Law by State",
       subtitle = "Darker colors indicate higher probabilities") +
  theme(legend.position = "bottom",
        panel.grid = element_blank(),      # Remove gridlines
        axis.text = element_blank(),       # Remove axis text
        axis.title = element_blank(),      # Remove axis titles
        axis.ticks = element_blank())      # Remove axis ticks
```

# Graphical Determinants of Cosporship

This section briefly describes how did cosponsorship vary over time.

From Figure 2 - Variation of Cosponsorship by Congress - we can observe that the values described above are derived by the frequent outliers observed in each of the congresses analyzed.

Because the 5 boxplots, containing data from 25th to 75th percentile, are generally close to 0, in the following graphs we show how mean and median varies, both when excluding and including the bills with 0 cosponsors. Overall, as explained, in this setting, the median appears more informative than the average. Then, the effective number of co-sponsors is around 4.

```{r graphs1, echo=FALSE, message=FALSE, warning=FALSE}
# Define relative paths for input and output files
## Create a box plot to show the distribution of cosponsors per bill over time
ggplot(bills_data, aes(x = as.factor(congress_id), y = n_cosponsor)) +
  geom_boxplot(aes(fill = as.factor(congress_id))) +
  labs(
    title = "Variation of Cosponsorship by Congress",
    x = "Congress",
    y = "Number of Cosponsors",
    fill = "Congress"
  ) +
  theme_minimal()
```


```{r graphs2, echo=FALSE, message=FALSE, warning=FALSE}

## Line plot showing the average number of cosponsors over time
# Calculate the average number of cosponsors over time (including zeros)
avg_cosponsors_per_year <- bills_data %>%
  group_by(year) %>%
  summarise(avg_cosponsors = mean(n_cosponsor, na.rm = TRUE))

# Calculate the average number of cosponsors over time (excluding zeros)
avg_cosponsors_per_year_no_zeros <- bills_data %>%
  filter(n_cosponsor > 0) %>%
  group_by(year) %>%
  summarise(avg_cosponsors_no_zeros = mean(n_cosponsor, na.rm = TRUE))

# Merge the two data frames by year
combined_avg_cosponsors <- avg_cosponsors_per_year %>%
  left_join(avg_cosponsors_per_year_no_zeros, by = "year")

# Plot both lines on the same graph
ggplot(combined_avg_cosponsors, aes(x = year)) +
  geom_line(aes(y = avg_cosponsors, color = "Including Zero Cosponsors"), size = 1.2) +
  geom_line(aes(y = avg_cosponsors_no_zeros, color = "Excluding Zero Cosponsors"), size = 1.2) +
  geom_point(aes(y = avg_cosponsors, color = "Including Zero Cosponsors"), size = 3) +
  geom_point(aes(y = avg_cosponsors_no_zeros, color = "Excluding Zero Cosponsors"), size = 3) +
  labs(
    title = "Average Number of Cosponsors Over Time",
    x = "Year",
    y = "Average Number of Cosponsors",
    color = "Legend"
  ) +
  scale_color_manual(values = c("Including Zero Cosponsors" = "#890089", "Excluding Zero Cosponsors" = "#108F10")) +
  theme_minimal()
```

```{r graphs3, echo=FALSE, message=FALSE, warning=FALSE}

# Calculate the average number of cosponsors over time (including zeros)
avg_cosponsors_per_year <- bills_data %>%
  group_by(year) %>%
  summarise(avg_cosponsors = median(n_cosponsor, na.rm = TRUE))

# Calculate the average number of cosponsors over time (excluding zeros)
avg_cosponsors_per_year_no_zeros <- bills_data %>%
  filter(n_cosponsor > 0) %>%
  group_by(year) %>%
  summarise(avg_cosponsors_no_zeros = median(n_cosponsor, na.rm = TRUE))

# Merge the two data frames by year
combined_avg_cosponsors <- avg_cosponsors_per_year %>%
  left_join(avg_cosponsors_per_year_no_zeros, by = "year")

# Plot both lines on the same graph
ggplot(combined_avg_cosponsors, aes(x = year)) +
  geom_line(aes(y = avg_cosponsors, color = "Including Zero Cosponsors"), size = 1.2) +
  geom_line(aes(y = avg_cosponsors_no_zeros, color = "Excluding Zero Cosponsors"), size = 1.2) +
  geom_point(aes(y = avg_cosponsors, color = "Including Zero Cosponsors"), size = 3) +
  geom_point(aes(y = avg_cosponsors_no_zeros, color = "Excluding Zero Cosponsors"), size = 3) +
  labs(
    title = "Median Number of Cosponsors Over Time",
    x = "Year",
    y = "Average Number of Cosponsors",
    color = "Legend"
  ) +
  scale_color_manual(values = c("Including Zero Cosponsors" = "#890089", "Excluding Zero Cosponsors" = "#108F10")) +
  theme_minimal()
```
# Determinants of Cosponsorship

```{r regs1, echo=FALSE, message=FALSE, warning=FALSE}
# Step 3 - Determinants of cosponsorship using OLS

# Define models
model1 <- lm(n_cosponsor ~ sponsor_party + factor(sponsor_state) + factor(congress_id), data = bills_data)
model2 <- lm(n_cosponsor ~ sponsor_party + majority + factor(sponsor_state) + factor(congress_id), data = bills_data)
model3 <- lm(n_cosponsor ~ sponsor_party + factor(sponsor_region) + factor(congress_id), data = bills_data)
model4 <- lm(n_cosponsor ~ sponsor_party + majority + factor(sponsor_region) + factor(congress_id), data = bills_data)

# Define custom labels for fixed effects
fixed_effects_labels <- list(
  "Fixed Effects: Sponsor's State" = c("Yes", "Yes", "No", "No"),
  "Fixed Effects: Sponsor's Region" = c("No", "No", "Yes", "Yes"),
  "Fixed Effects: Congress Year" = c("Yes", "Yes", "Yes", "Yes")
)

# Create a table with Stargazer
stargazer(model1, model2, model3, model4,
          type = "text",  # Change to "html" or "latex" if needed
          title = "Regression Results",
          covariate.labels = c("Sponsor's Party", "Majority"),
          add.lines = list(
            c("Fixed Effects: Sponsor's State", fixed_effects_labels[["Fixed Effects: Sponsor's State"]]),
            c("Fixed Effects: Sponsor's Region", fixed_effects_labels[["Fixed Effects: Sponsor's Region"]]),
            c("Fixed Effects: Congress Year", fixed_effects_labels[["Fixed Effects: Congress Year"]])
          ),
          omit = c("factor(sponsor_state)*", "factor(sponsor_region)*", "factor(congress_id)*"),  # Omit fixed effects
          omit.stat = c("f", "ser", "ll", "rsq"),  # Omit statistics you don't need
          star.cutoffs = c(0.05, 0.01, 0.001),  # Significance levels
          dep.var.labels = "N. Cosponsors",
          style = "default")
```

```{r regs2, echo=FALSE, message=FALSE, warning=FALSE}

# Define OLS models
ols_model1 <- lm(is_passed ~ n_cosponsor + sponsor_party + majority + factor(sponsor_state) + factor(congress_id), data = bills_data)
ols_model2 <- lm(is_passed ~ n_cosponsor + same_party_state + sponsor_party + majority + factor(sponsor_state) + factor(congress_id), data = bills_data)
ols_model3 <- lm(is_law ~ n_cosponsor + factor(sponsor_state) + sponsor_party + majority + factor(congress_id), data = bills_data)
ols_model4 <- lm(is_law ~ n_cosponsor + same_party_state + sponsor_party + majority + factor(sponsor_state) + factor(congress_id), data = bills_data)

# Define custom labels for fixed effects
fixed_effects_labels_ols <- list(
  "Fixed Effects: Sponsor's State" = c("Yes", "Yes", "Yes", "Yes"),
  "Fixed Effects: Congress Year" = c("Yes", "Yes", "Yes", "Yes")
)

# Create OLS table with Stargazer
stargazer(ols_model1, ols_model2, ols_model3, ols_model4,
          type = "text",  # Change to "html" or "latex" if needed
          title = "Regression Results (LPM)",
          covariate.labels = c("Num Cosponsor", "Same Party-State", "Sponsor's Party", "Majority"),
          add.lines = list(
            c("Fixed Effects: Sponsor's State", fixed_effects_labels_ols[["Fixed Effects: Sponsor's State"]]),
            c("Fixed Effects: Congress Year", fixed_effects_labels_ols[["Fixed Effects: Congress Year"]])
          ),
          omit = c("factor(sponsor_state)*", "factor(congress_id)*"),  # Omit fixed effects
          omit.stat = c("f", "ser", "ll", "rsq"),  # Omit statistics you don't need
          dep.var.labels = c("Prob(Passed House)", "Prob(Law)"),
          star.cutoffs = c(0.05, 0.01, 0.001),  # Significance levels
          style = "default")
```

```{r regs3, echo=FALSE, message=FALSE, warning=FALSE}

# Define Probit models
probit_model1 <- glm(is_passed ~ n_cosponsor + sponsor_party + majority + factor(sponsor_state) + factor(congress_id), family = binomial(link = "probit"), data = bills_data)
probit_model2 <- glm(is_passed ~ n_cosponsor + same_party_state + sponsor_party + majority + factor(sponsor_state) + factor(congress_id), family = binomial(link = "probit"), data = bills_data)
probit_model3 <- glm(is_law ~ n_cosponsor + factor(sponsor_state) + sponsor_party + majority + factor(congress_id), family = binomial(link = "probit"), data = bills_data)
probit_model4 <- glm(is_law ~ n_cosponsor + same_party_state + sponsor_party + majority + factor(sponsor_state) + factor(congress_id), family = binomial(link = "probit"), data = bills_data)


# Define custom labels for fixed effects
fixed_effects_labels_ols <- list(
  "Fixed Effects: Sponsor's State" = c("Yes", "Yes", "Yes", "Yes"),
  "Fixed Effects: Congress Year" = c("Yes", "Yes", "Yes", "Yes")
)

# Create OLS table with Stargazer
stargazer(probit_model1, probit_model2, probit_model3, probit_model4,
          type = "text",  # Change to "html" or "latex" if needed
          title = "Regression Results (Probit)",
          covariate.labels = c("Num Cosponsor", "Same Party-State", "Sponsor's Party", "Majority"),
          add.lines = list(
            c("Fixed Effects: Sponsor's State", fixed_effects_labels_ols[["Fixed Effects: Sponsor's State"]]),
            c("Fixed Effects: Congress Year", fixed_effects_labels_ols[["Fixed Effects: Congress Year"]])
          ),
          omit = c("factor(sponsor_state)*", "factor(congress_id)*"),  # Omit fixed effects
          omit.stat = c("f", "ser", "ll", "rsq"),  # Omit statistics you don't need
          dep.var.labels = c("Prob(Passed House)", "Prob(Law)"),
          star.cutoffs = c(0.05, 0.01, 0.001),  # Significance levels
          style = "default")
```
