---
title: "PP4RS Report - *Congress Bills Cosponsorship*"
author: "Lorenzo Maria Casale & Matteo Machiorlatti"
date: "15/09/2024"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
# Load required libraries
library(readr)
library(dplyr)
library(ggplot2)
library(lmtest)
library(ivreg)
library(knitr)
library(kableExtra)
library(tidyr)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(sandwich)
library(stargazer)
library(rmarkdown)
library(sandwich)  
library(lmtest)    
library(devtools)
library(stats)
```


This research report examines the determinants of cosponsorship at the bill level within the United States House of Representatives during the 2010s.

We collected data on bills presented to the House of Representatives throughout the 2010s. The **data collection** process was automated through the scraping of the [official website](https://www.congress.gov/) of the Congress. For each bill, we gathered the following information:

- **Congress Session ID:** Identifying the specific session in which the bill was introduced.
- **Bill-Specific Information:** The bill's URL, title, the committee it was assigned to (e.g., Energy or Housing), and its status (e.g., Introduced, Passed House, Became Law).
- **Sponsor Details:** Information about the member who introduced the bill, including their party affiliation, state of election, and district.
- **Cosponsor Information:** Data on members who cosponsored the bill. We collected the total number of cosponsors and noted how many shared the same party affiliation and/or state of origin as the sponsor.

```{r dataprep, echo=FALSE, message=FALSE, warning=FALSE}

input_file <- file.path(dirname(getwd()), "data", "bills_data_final.csv")

## Appending all files
bills_data <- read.csv(input_file)

## Adding 'year' column based on 'congress_id'
bills_data <- bills_data %>%
  mutate(year = case_when(
    congress_id == 112 ~ "2011-2012",
    congress_id == 113 ~ "2013-2014",
    congress_id == 114 ~ "2015-2016",
    congress_id == 115 ~ "2017-2018",
    congress_id == 116 ~ "2019-2020"
  ))

## Creating Census Region
W <- c("AK", "AZ", "CA", "CO", "HI", "ID", "MT", "NV", "NM", "OR", "UT", "WA", "WY")
S <- c("AL", "AR", "DE", "FL", "GA", "KY", "LA", "MD", "MS", "NC", "OK", "SC", "TN", "TX", "VA", "WV")
MW <- c("IL", "IN", "IA", "KS", "MI", "MN", "MO", "NE", "ND", "OH", "SD", "WI")
NE <- c("CT", "ME", "MA", "NH", "NJ", "NY", "PA", "RI", "VT")

# Combine lists into a named list
All <- list(W = W, S = S, MW = MW, NE = NE)
Reg <- c("West", "South", "Midwest", "Northeast")

# Assume bills_data is your data frame with a column `sponsor_state`
bills_data$sponsor_region <- NA

# Update the region based on state abbreviations
for (reg in names(All)) {
  bills_data$sponsor_region[bills_data$sponsor_state %in% All[[reg]]] <- reg
}

# Set any remaining NA values to "Others"
bills_data$sponsor_region[is.na(bills_data$sponsor_region)] <- "Others"

# Create is_law variable
bills_data$is_law <- ifelse(bills_data$status %in% c("Became Law", "Became Private Law"), 1, 0)

# Create is_passed variable
bills_data$is_passed <- ifelse(bills_data$status %in% c("Became Law", "Became Private Law", "Vetoed by President", "Failed to pass over veto", "Resolving Differences", "Passed House", "Passed Senate"), 1, 0)
```

# Descriptive Statistics

### Overview by Sponsor's Party

**Table 1** shows the number of bills by sponsor's party. Due to the negligible number of bills sponsored by independents (I) and liberals (L), we will from now on only focus on Democrats (D) and Republicans (R)

```{r datadescr0, echo=FALSE, message=FALSE, warning=FALSE}
## Descriptive statistics with number of bills by sponsor_party
descriptive_stats <- bills_data %>% 
  group_by(sponsor_party) %>%
  summarise(
    `N. Bills` = n()  # Count of bills by sponsor_party
  )

descriptive_stats %>%
  kbl(caption = "Descriptive Statistics of Bill Data by Sponsor Party", digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE) %>%
  add_header_above(c(" " = 1, "Descriptive Stats" = 1)) %>%
  row_spec(0, bold = TRUE, extra_css = "border-bottom: 2px solid;")


bills_data <- bills_data %>%
  filter(sponsor_party %in% c("D", "R"))

bills_data <- bills_data %>%
  mutate(majority = case_when(
    sponsor_party == "R" & congress_id %in% c(112, 113, 114, 115) ~ 1,
    sponsor_party == "D" & congress_id == 116 ~ 1,
    TRUE ~ 0
  ))
```

### Cosponsorship Patterns

**Table 2** provides summary statistics on cosponsorship across all bills, highlighting the average number of cosponsors and the breakdown by party and state affiliations.

The majority of cosponsors share the same party as the bill's sponsor, which aligns with expected party solidarity. On the other hand, only a small fraction of cosponsors (about 1.5%) come from the same state and party as the sponsor, indicating that geographic factors are less influential than party affiliation in garnering support.

```{r datadescr1, echo=FALSE, message=FALSE, warning=FALSE}
## Descriptive statistics all sample
descriptive_stats <- bills_data %>% 
  summarise(
    `Avg. N. Cosponsor` = mean(n_cosponsor, na.rm = TRUE),
    `Avg. N. Same Party Cosp.` = mean(same_party, na.rm = TRUE),
    `Avg. N. Same State Cosp.` = mean(same_state, na.rm = TRUE),
    `Avg. N. Same (Party x State) Cosp.` = mean(same_party_state, na.rm = TRUE)
  )
descriptive_stats %>%
  kbl(caption = "Descriptive Statistics of Bill Data", digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE) %>%
  add_header_above(c(" " = 1, "Descriptive Stats" = 3)) %>%
  row_spec(0, bold = TRUE, extra_css = "border-bottom: 2px solid;")
```

### Bill Status Distribution

In **Table 3**, we show that only a small portion - slightly more than 3% - of proposed bills actually becomes law. It must however be noticed that about 10% of the bills manages to overcome the first obstacle, namely the Congress' House. The rest is just merely introduced and no further steps are taken.

```{r datadescr1b, echo=FALSE, message=FALSE, warning=FALSE}

## Descriptive statistics all sample - Passing Probability
status_probs <- bills_data %>%
  group_by(status) %>%
  summarise(`Probability` = n() / nrow(bills_data)) %>%
  mutate(status = factor(status, levels = c("Became Law", "Became Private Law", "Vetoed by President", 
                                            "Failed to pass over veto", "Resolving Differences", 
                                            "Passed House", "Passed Senate", "Failed House", "Introduced"))) %>%
  arrange(status)  # Arrange based on the custom factor order

status_probs %>%
  kbl(caption = "Probability of Each Bill Status", digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE) %>%
  row_spec(0, bold = TRUE, extra_css = "border-bottom: 2px solid;")
```

### Analysis by Congress (i.e. time)

**Tables 4** and **5** replicate the analysis of Tables 2 and 3, but now splitting the data by congress (which in this case coincide with splitting by year).

```{r datadescr2, echo=FALSE, message=FALSE, warning=FALSE}

## Descriptive statistics by congress_id
descriptive_stats_by_congress <- bills_data %>% 
  group_by(congress_id, year) %>%
  summarise(
    `Avg. N. Cosponsor` = mean(n_cosponsor, na.rm = TRUE),
    `Avg. N. Same Party Cosp.` = mean(same_party, na.rm = TRUE),
    `Avg. N. Same State Cosp.` = mean(same_state, na.rm = TRUE),
    `Avg. N. Same (Party x State) Cosp.` = mean(same_party_state, na.rm = TRUE)
  )

descriptive_stats_by_congress %>%
  kbl(caption = "Descriptive Statistics of Bill Data by Congress and Year", digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE)
```

```{r datadescr3, echo=FALSE, message=FALSE, warning=FALSE}

## Descriptive statistics by congress_id - Passing Probability

status_probs_by_congress <- bills_data %>%
  group_by(congress_id, year, status) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(congress_id, year) %>%
  mutate(total = sum(count), 
         `Probability` = count / total) %>%
  filter(status %in% c("Became Law", "Passed House", "Passed Senate", "Failed House", "Introduced")) %>%
  select(-count, -total)  # Remove intermediate columns if you don't need them


status_probs_wide <- status_probs_by_congress %>%
  unite("congress_year", congress_id, year, sep = " (") %>%
  mutate(congress_year = paste0(congress_year, ")")) %>%
  pivot_wider(
    names_from = congress_year, 
    values_from = Probability,
    values_fill = 0  # Fill any missing combinations with 0
  ) %>%
  arrange(match(status, c("Became Law", "Passed House", "Passed Senate", "Failed House", "Introduced")))

status_probs_wide %>%
  kbl(caption = "Probability of Each Bill Status by Congress and Year", digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE)
```

### Probability of Bills Becoming Law by Sponsor's Party

**Table 6** compares the probability of bills becoming law based on the sponsor's party and whether they were the majority in the House. 

Overall, in the period we analyzed, Republicans had a much higher success rate in passing bills compared to Democrats. This may be at least partially explained by the Republicans being the majority party in most of the Congresses in our sample and this may have played a central role. The fact that Democrats led in the final Congress and still saw a low share of bills that passed may be due to persistence. It would be interesting to increase the lenght of our sample and check whether there was an inversion in the next Congresses. 

```{r datadescr4, echo=FALSE, message=FALSE, warning=FALSE}

## Calculate the probability of a bill becoming law by party and congress

prob_by_party_congress <- bills_data %>%
  filter(sponsor_party %in% c("R", "D")) %>%
  group_by(congress_id, year, sponsor_party) %>%
  summarise(`Prob. Becoming Law` = mean(status == "Became Law", na.rm = TRUE), .groups = 'drop') %>%
  pivot_wider(names_from = sponsor_party, values_from = `Prob. Becoming Law`, values_fill = list(`Prob. Becoming Law` = 0)) %>%
  rename(Republican = R, Democrat = D)

prob_by_party_congress <- prob_by_party_congress %>%
  mutate(
    Republican = ifelse(congress_id != 116, cell_spec(round(Republican, 3), bold = TRUE), round(Republican, 3)),
    Democrat = ifelse(congress_id == 116, cell_spec(round(Democrat, 3), bold = TRUE), round(Democrat, 3))
  )

prob_by_party_congress %>%
  kbl(escape = FALSE, caption = "Probability of Bills Becoming Law by Party and Congress") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE) %>%
  add_header_above(c(" " = 2, "Probability of Becoming Law" = 2)) %>%
  row_spec(0, bold = TRUE, extra_css = "border-bottom: 2px solid;")
```

### Geographic Variation in Legislative Success

**Figure 1** illustrates the probability of bills becoming law by the sponsor's state, with states grouped by Census regions. Each Census is recognizable because of each state's border. In yellow, there are the west states, in red the midwest, in green the south states, and finally in violet the north-east states.

From the map, no clear regional differences are easily identifiable - except for a couple of states with higher values such as Idaho and Mississippi. This would suggest that factors other than geographic location play a more substantial role.


```{r datadescr5, echo=FALSE, message=FALSE, warning=FALSE}

##  Load spatial data for US states
us_states <- rnaturalearth::ne_states(country = "United States of America", returnclass = "sf")

## Ensure state abbreviations in the bills_data match those in the spatial data
us_states <- us_states %>%
  mutate(sponsor_state = state.abb[match(name, state.name)]) %>%
  select(sponsor_state, geometry)

## Merge the state map with bills data
state_map <- us_states %>%
  left_join(bills_data %>%
              group_by(sponsor_state) %>%
              summarise(`Prob. Becoming Law` = mean(status == "Became Law", na.rm = TRUE), 
                        sponsor_region = first(sponsor_region)),
            by = "sponsor_state")

## Remove Alaska (AK) and Hawaii (HI) from the spatial data and bills data
state_map <- state_map %>%
  filter(!sponsor_state %in% c("AK", "HI"))

## Define the darkest color for each region
region_colors <- c(
  "W" = "#FFC500",   # Dark Orange for West
  "S" = "#009900",  # Dark Green for South
  "MW" = "#FF0000", # Dark Brown for Midwest
  "NE" = "#9999FF" # Dark Cyan for Northeast
)

## Add border colors to the data
state_map <- state_map %>%
  mutate(border_color = region_colors[sponsor_region])

## Create the map
ggplot(data = state_map) +
  geom_sf(aes(fill = `Prob. Becoming Law`, color = border_color), lwd = 1) +  # Increased border size
  scale_fill_gradientn(colors = c("#E0FFFF", "#36454F"), name = "Probability", labels = scales::number_format(accuracy = 0.01)
) + # Apply the gradient scale for probability
  scale_color_identity() +  # Use the colors defined in the data
  theme_minimal() +
  labs(title = "Probability of Bills Becoming Law by State",
       subtitle = "Darker colors indicate higher probabilities") +
  theme(legend.position = "bottom",
        panel.grid = element_blank(),      # Remove gridlines
        axis.text = element_blank(),       # Remove axis text
        axis.title = element_blank(),      # Remove axis titles
        axis.ticks = element_blank())      # Remove axis ticks
```

# Graphical Analysis of Cosponsorship Determinants

This section explores how cosponsorship patterns have evolved over time.

### Variation of Cosponsorship by Congress

**Figure 2** displays boxplots of cosponsorship numbers across different Congress sessions. It clearly points to the existence of large outliers in the number of cosponsors and - hence - to the need to use medians instead of averages for summary statistics.

```{r graphs1, echo=FALSE, message=FALSE, warning=FALSE}
# Define relative paths for input and output files
## Create a box plot to show the distribution of cosponsors per bill over time
ggplot(bills_data, aes(x = as.factor(congress_id), y = n_cosponsor)) +
  geom_boxplot(aes(fill = as.factor(congress_id))) +
  labs(
    title = "Variation of Cosponsorship by Congress",
    x = "Congress",
    y = "Number of Cosponsors",
    fill = "Congress"
  ) +
  theme_minimal()
```

**Figures 3** and **4** show the mean and median number of cosponsors over time, both including and excluding bills with zero cosponsors.

```{r graphs2, echo=FALSE, message=FALSE, warning=FALSE}

## Line plot showing the average number of cosponsors over time
# Calculate the average number of cosponsors over time (including zeros)
avg_cosponsors_per_year <- bills_data %>%
  group_by(year) %>%
  summarise(avg_cosponsors = mean(n_cosponsor, na.rm = TRUE))

# Calculate the average number of cosponsors over time (excluding zeros)
avg_cosponsors_per_year_no_zeros <- bills_data %>%
  filter(n_cosponsor > 0) %>%
  group_by(year) %>%
  summarise(avg_cosponsors_no_zeros = mean(n_cosponsor, na.rm = TRUE))

# Merge the two data frames by year
combined_avg_cosponsors <- avg_cosponsors_per_year %>%
  left_join(avg_cosponsors_per_year_no_zeros, by = "year")

# Plot both lines on the same graph
ggplot(combined_avg_cosponsors, aes(x = year)) +
  geom_line(aes(y = avg_cosponsors, color = "Including Zero Cosponsors"), size = 1.2) +
  geom_line(aes(y = avg_cosponsors_no_zeros, color = "Excluding Zero Cosponsors"), size = 1.2) +
  geom_point(aes(y = avg_cosponsors, color = "Including Zero Cosponsors"), size = 3) +
  geom_point(aes(y = avg_cosponsors_no_zeros, color = "Excluding Zero Cosponsors"), size = 3) +
  labs(
    title = "Average Number of Cosponsors Over Time",
    x = "Year",
    y = "Average Number of Cosponsors",
    color = "Legend"
  ) +
  scale_color_manual(values = c("Including Zero Cosponsors" = "#890089", "Excluding Zero Cosponsors" = "#108F10")) +
  theme_minimal()
```

```{r graphs3, echo=FALSE, message=FALSE, warning=FALSE}

# Calculate the average number of cosponsors over time (including zeros)
avg_cosponsors_per_year <- bills_data %>%
  group_by(year) %>%
  summarise(avg_cosponsors = median(n_cosponsor, na.rm = TRUE))

# Calculate the average number of cosponsors over time (excluding zeros)
avg_cosponsors_per_year_no_zeros <- bills_data %>%
  filter(n_cosponsor > 0) %>%
  group_by(year) %>%
  summarise(avg_cosponsors_no_zeros = median(n_cosponsor, na.rm = TRUE))

# Merge the two data frames by year
combined_avg_cosponsors <- avg_cosponsors_per_year %>%
  left_join(avg_cosponsors_per_year_no_zeros, by = "year")

# Plot both lines on the same graph
ggplot(combined_avg_cosponsors, aes(x = year)) +
  geom_line(aes(y = avg_cosponsors, color = "Including Zero Cosponsors"), size = 1.2) +
  geom_line(aes(y = avg_cosponsors_no_zeros, color = "Excluding Zero Cosponsors"), size = 1.2) +
  geom_point(aes(y = avg_cosponsors, color = "Including Zero Cosponsors"), size = 3) +
  geom_point(aes(y = avg_cosponsors_no_zeros, color = "Excluding Zero Cosponsors"), size = 3) +
  labs(
    title = "Median Number of Cosponsors Over Time",
    x = "Year",
    y = "Average Number of Cosponsors",
    color = "Legend"
  ) +
  scale_color_manual(values = c("Including Zero Cosponsors" = "#890089", "Excluding Zero Cosponsors" = "#108F10")) +
  theme_minimal()
```

# Regression analyses

We finally conducted regression analyses - LPM and Probit - to identify factors influencing cosponsorship and legislative success. This part of the analysis is mostly to showcase how to run regressions and build tables in Rstudio through Snakemake automation, but it should not be considered as a rigorous investigation - as it is indeed flawed in many potential ways (first of all endogeneity, but also omitted variable bias, ...). 

We will hence not discuss the results, but only present the tables themselves.

**Table 7** uses a linear regression analysis (OLS) to investigate the determinants of cosponsorship.

```{r regs1, echo=FALSE, message=FALSE, warning=FALSE}
# Step 3 - Determinants of cosponsorship using OLS

# Define models
model1 <- lm(n_cosponsor ~ sponsor_party + factor(sponsor_state) + factor(congress_id), data = bills_data)
model2 <- lm(n_cosponsor ~ sponsor_party + majority + factor(sponsor_state) + factor(congress_id), data = bills_data)
model3 <- lm(n_cosponsor ~ sponsor_party + factor(sponsor_region) + factor(congress_id), data = bills_data)
model4 <- lm(n_cosponsor ~ sponsor_party + majority + factor(sponsor_region) + factor(congress_id), data = bills_data)

# Define custom labels for fixed effects
fixed_effects_labels <- list(
  "Fixed Effects: Sponsor's State" = c("Yes", "Yes", "No", "No"),
  "Fixed Effects: Sponsor's Region" = c("No", "No", "Yes", "Yes"),
  "Fixed Effects: Congress Year" = c("Yes", "Yes", "Yes", "Yes")
)

# Create a table with Stargazer
stargazer(model1, model2, model3, model4,
          type = "text",  # Change to "html" or "latex" if needed
          title = "Regression Results",
          covariate.labels = c("Sponsor's Party", "Majority"),
          add.lines = list(
            c("Fixed Effects: Sponsor's State", fixed_effects_labels[["Fixed Effects: Sponsor's State"]]),
            c("Fixed Effects: Sponsor's Region", fixed_effects_labels[["Fixed Effects: Sponsor's Region"]]),
            c("Fixed Effects: Congress Year", fixed_effects_labels[["Fixed Effects: Congress Year"]])
          ),
          omit = c("factor(sponsor_state)*", "factor(sponsor_region)*", "factor(congress_id)*"),  # Omit fixed effects
          omit.stat = c("f", "ser", "ll", "rsq"),  # Omit statistics you don't need
          star.cutoffs = c(0.05, 0.01, 0.001),  # Significance levels
          dep.var.labels = "N. Cosponsors",
          style = "default")
```

**Table 8** and **9** use - respectively - a linear regression analysis (OLS) and a Probit to assess how the number of cosponsors affect the probability of a bill to pass the House (columns 1 & 2) and to become law (3 and 4)

```{r regs2, echo=FALSE, message=FALSE, warning=FALSE}

# Define OLS models
ols_model1 <- lm(is_passed ~ n_cosponsor + sponsor_party + majority + factor(sponsor_state) + factor(congress_id), data = bills_data)
ols_model2 <- lm(is_passed ~ n_cosponsor + same_party_state + sponsor_party + majority + factor(sponsor_state) + factor(congress_id), data = bills_data)
ols_model3 <- lm(is_law ~ n_cosponsor + factor(sponsor_state) + sponsor_party + majority + factor(congress_id), data = bills_data)
ols_model4 <- lm(is_law ~ n_cosponsor + same_party_state + sponsor_party + majority + factor(sponsor_state) + factor(congress_id), data = bills_data)

# Define custom labels for fixed effects
fixed_effects_labels_ols <- list(
  "Fixed Effects: Sponsor's State" = c("Yes", "Yes", "Yes", "Yes"),
  "Fixed Effects: Congress Year" = c("Yes", "Yes", "Yes", "Yes")
)

# Create OLS table with Stargazer
stargazer(ols_model1, ols_model2, ols_model3, ols_model4,
          type = "text",  # Change to "html" or "latex" if needed
          title = "Regression Results (LPM)",
          covariate.labels = c("Num Cosponsor", "Same Party-State", "Sponsor's Party", "Majority"),
          add.lines = list(
            c("Fixed Effects: Sponsor's State", fixed_effects_labels_ols[["Fixed Effects: Sponsor's State"]]),
            c("Fixed Effects: Congress Year", fixed_effects_labels_ols[["Fixed Effects: Congress Year"]])
          ),
          omit = c("factor(sponsor_state)*", "factor(congress_id)*"),  # Omit fixed effects
          omit.stat = c("f", "ser", "ll", "rsq"),  # Omit statistics you don't need
          dep.var.labels = c("Prob(Passed House)", "Prob(Law)"),
          star.cutoffs = c(0.05, 0.01, 0.001),  # Significance levels
          style = "default")
```

```{r regs3, echo=FALSE, message=FALSE, warning=FALSE}

# Define Probit models
probit_model1 <- glm(is_passed ~ n_cosponsor + sponsor_party + majority + factor(sponsor_state) + factor(congress_id), family = binomial(link = "probit"), data = bills_data)
probit_model2 <- glm(is_passed ~ n_cosponsor + same_party_state + sponsor_party + majority + factor(sponsor_state) + factor(congress_id), family = binomial(link = "probit"), data = bills_data)
probit_model3 <- glm(is_law ~ n_cosponsor + factor(sponsor_state) + sponsor_party + majority + factor(congress_id), family = binomial(link = "probit"), data = bills_data)
probit_model4 <- glm(is_law ~ n_cosponsor + same_party_state + sponsor_party + majority + factor(sponsor_state) + factor(congress_id), family = binomial(link = "probit"), data = bills_data)


# Define custom labels for fixed effects
fixed_effects_labels_ols <- list(
  "Fixed Effects: Sponsor's State" = c("Yes", "Yes", "Yes", "Yes"),
  "Fixed Effects: Congress Year" = c("Yes", "Yes", "Yes", "Yes")
)

# Create OLS table with Stargazer
stargazer(probit_model1, probit_model2, probit_model3, probit_model4,
          type = "text",  # Change to "html" or "latex" if needed
          title = "Regression Results (Probit)",
          covariate.labels = c("Num Cosponsor", "Same Party-State", "Sponsor's Party", "Majority"),
          add.lines = list(
            c("Fixed Effects: Sponsor's State", fixed_effects_labels_ols[["Fixed Effects: Sponsor's State"]]),
            c("Fixed Effects: Congress Year", fixed_effects_labels_ols[["Fixed Effects: Congress Year"]])
          ),
          omit = c("factor(sponsor_state)*", "factor(congress_id)*"),  # Omit fixed effects
          omit.stat = c("f", "ser", "ll", "rsq"),  # Omit statistics you don't need
          dep.var.labels = c("Prob(Passed House)", "Prob(Law)"),
          star.cutoffs = c(0.05, 0.01, 0.001),  # Significance levels
          style = "default")
```

As a general and intuitive takeaway, the number of cosponsors seem to have a positive effect on the probability of a bill both passing the House and becoming law. However, as mentioned above, here there is - at least some - endogeneity at play. For instance, it is very likely that high quality bills have a larger number of cosponsors as well as a higher probability of success, and this may be what our results is capturing. The same applies to bills that are more "politically trendy" and expected from the public opinion.
